---
title: "Getting Started with googlesites"
author: "Steven Mortimer"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Getting Started with googlesites}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
NOT_CRAN <- identical(tolower(Sys.getenv("NOT_CRAN")), "true")
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  purl = NOT_CRAN,
  eval = NOT_CRAN
)
```

First, we load `googlesites` and specify the domain and site name we'll be working 
with. Creating a completely new site is only available to GSuite users (formerly 
known as Google Apps), so you should have already created this classic site using the 
web UI and know the domain and site name to plug into the package options. These 
options allow you to edit the site without specifying it explicitly on each request.

```{r load-package}
library(googlesites)
options(googlesites.site_domain = "site")
options(googlesites.site_name = "testrgooglsites")
```

Second, you need to use the `googleAuthR` package to get your OAuth2.0 token 
to make edits to your site from the R script.

```{r authenticate}
library(googleAuthR)
options(googleAuthR.scopes.selected = "https://sites.google.com/feeds/")
gar_auth()
```

### Adding a Page

The package comes with ... 

```{r adding-page}
sample_html <- system.file("extdata", "sample-doc.html", package="googlesites")
add_html_page(page_xhtml_source = sample_html,
              page_title = 'Post with GIF',
              page_custom_url = 'post-with-gif',
              overwrite=TRUE)
```

### Finding Content

The package comes with ... 

```{r finding-content}
find_content(value_to_match='Post with GIF', 
             field_to_match='title', 
             content_category='webpage')
```

### Adding an Attachment

You can ...

```{r adding-attachment, eval=FALSE}
pdf_cheatsheet <- 'https://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf'
download.file(pdf_cheatsheet, 'rmarkdown-cheatsheet-2.0.pdf', mode="wb")

# uploading something to that page
upload_file_to_site(local_file_path = "rmarkdown-cheatsheet-2,0.pdf", 
                    file_summary = 'R Markdown is an authoring format that makes it 
                    easy to write reusable reports with R. You combine your R code 
                    with narration written in markdown (an easy-to-write plain text format) 
                    and then export the results as an html, pdf, or Word file. You can 
                    even use R Markdown to build interactive documents and slideshows. 
                    Updated 02/16.',
                    parent_page_id = find_content(value_to_match='Post with GIF', 
                                                  field_to_match='title')$id)
```

```{r real-adding-attachment, include=FALSE}
upload_file_to_site(local_file_path = system.file("extdata", "files", "rmarkdown-cheatsheet-2.0.pdf", package="googlesites"), 
                    file_summary = 'R Markdown is an authoring format that makes it 
                    easy to write reusable reports with R. You combine your R code 
                    with narration written in markdown (an easy-to-write plain text format) 
                    and then export the results as an html, pdf, or Word file. You can 
                    even use R Markdown to build interactive documents and slideshows. 
                    Updated 02/16.',
                    parent_page_id = find_content(value_to_match='Post with GIF', 
                                                  field_to_match='title')$id)
```

### Deleting Attachment

You can ...

```{r deleting-attachment}
# deleting the attachment
delete_content(id = find_content(value_to_match='rmarkdown-cheatsheet-2.0.pdf',
                                 field_to_match='title', 
                                 content_category='attachment')$id)
```

### Deleting Page

You can ...

```{r deleting-page}
# deleting that page
delete_content(id = find_content(value_to_match='testwebp',
                                 field_to_match='title')$id)
```
